%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 3.0 (December 17, 2022)
%
% This template originates from:
% https://www.LaTeXTemplates.com
%
% Author:
% Vel (vel@latextemplates.com)
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% License:
% CC BY-NC-SA 4.0 (https://creativecommons.org/licenses/by-nc-sa/4.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-----------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-----------------------------------------------------------------

\documentclass[
	10.5pt, % Default font size, can use 10pt, 11pt or 12pt
]{resume} % Use the resume class

\usepackage{ebgaramond} % Use the EB Garamond font
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage{xcolor}
\usepackage[T1]{fontenc}

\usepackage{ifthen}

% Define role and clearance flags
\newboolean{Frontend}
\newboolean{Backend}
\newboolean{Data}
\newboolean{Clearance}

% Default: all false
\setboolean{Frontend}{false}
\setboolean{Backend}{false}
\setboolean{Data}{false}
\setboolean{Clearance}{false}

\input{config.tex}

%------------------------------------------------

\name{Michael T. Moen} % Your name to appear at the top

% \address{St. Louis, MO \\ moenmichael02@gmail.com \\ (636) 633-3173 \\ \underline{\href{https://www.linkedin.com/in/mtmoen/}{in/mtmoen/}} \\ \underline{\href{https://github.com/MoenMi}{github.com/MoenMi}} \\ \underline{\href{https://mtmoen.com}{mtmoen.com}}}

\address{St. Louis, MO \\ moenmichael02@gmail.com \\ (XXX) XXX-XXXX \\ \underline{\href{https://www.linkedin.com/in/mtmoen/}{linkedin.com/in/mtmoen/}}}

\ifthenelse{\boolean{Clearance}}{
	\address{U.S. Citizen \\ Active Top Secret Clearance with SCI (TS/SCI)}
}{}

%-----------------------------------------------------------------

\begin{document}

%-----------------------------------------------------------------
%	EDUCATION SECTION
%-----------------------------------------------------------------

\begin{rSection}{Education}

	% \textbf{The University of Alabama}, \textit{M.S. in Applied Statistics, Tuscaloosa, AL} - 3.67/4.00 GPA \hfill May 2026

	% \textbf{The University of Alabama} \hfill May 2026 \\
	% \textit{M.S. in Applied Statistics} - 3.67/4.00 GPA \hfill \textit{Tuscaloosa, AL}
	% \vspace{-0.2em}
	% \begin{rEducation}{M.S. in Applied Statistics}{The University of Alabama}{Tuscaloosa, AL}{3.67/4.00}{May 2026}
	% \end{rEducation}
	
	% \textbf{The University of Alabama}, \textit{Honors B.S. in Computer Science \& Mathematics, Tuscaloosa, AL} - 3.89/4.00 GPA \hfill May 2026
	% \vspace{-0.2em}
	
	% \textbf{The University of Alabama} \hfill May 2026 \\
	% \textit{Honors B.S. in Computer Science \& Mathematics} - 3.89/4.00 GPA \hfill \textit{Tuscaloosa, AL} \\
	% National Merit Scholarship Recipient (5 years full tuition, 4 years housing + stipend)
	% \vspace{-0.2em}
	
	\begin{rEducation}{M.S. in Applied Statistics}{The University of Alabama}{Tuscaloosa, AL}{3.67/4.00}{May 2026}
	\end{rEducation}
	
	\begin{rEducation}{B.S. in Computer Science \& Mathematics}{The University of Alabama}{Tuscaloosa, AL}{3.89/4.00}{May 2026}
	\end{rEducation}
	% \begin{rEducation2}{B.S. in Computer Science \& Mathematics}{The University of Alabama}{Tuscaloosa, AL}{3.89/4.00}{May 2026}
	% 	\item National Merit Scholar, Accelerated Masters Program, Honors College, Pi Mu Epsilon
	% \end{rEducation2}

	\vspace{0.25em}
	
\end{rSection}

%-----------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%-----------------------------------------------------------------

\begin{rSection}{Experience}

	\begin{rSubsection2}{The University of Alabama Libraries}{January 2023 - Present}{Research Computing Student Lead}{Tuscaloosa, AL}
		\item Provide software development and data analysis support; assist with coding in Python, C++, R, Java, HTML, CSS, and more.
		\item Publish 20+ tutorials on accessing and analyzing REST APIs using Python and R, managing and reviewing GitHub Pages site content.
		\item Design and teach workshops covering programming, data analysis, and machine learning using Python, R, and scikit-learn.
		\item Built a full-stack web application using a Python Flask backend and a JavaScript, HTML, and CSS frontend for retrieving CEO pay data.
	\end{rSubsection2}

	\begin{rSubsection2}{Veterans United Home Loans}{May 2025 - Present}{MLOps Engineer Intern}{Remote}
		\item Use Python FastAPI to develop and maintain tools for machine learning (ML) model deployment and development.
		\item Develop and maintain scalable ML infrastructure using Docker, Kubernetes, SQLAlchemy, Azure, and Grafana.
	\end{rSubsection2}

	\ifthenelse{\boolean{Frontend}}{
		\begin{rSubsection2}{Bowfin Tech}{January 2025 - May 2025}{Web Developer Intern}{Remote}
			\item Built a client's website using WordPress and Elementor, implementing responsive web design for mobile and desktop users.
			\item Implemented user tracking by integrating Google Tag Manager and Google Analytics with Google Ads and Meta Pixel.
		\end{rSubsection2}
	}{}

	\begin{rSubsection2}{Northrop Grumman}{June 2024 - August 2024}{Cyber Software Engineer Intern}{San Antonio, TX}
		\item Automated the installation and updating of applications on 20+ Windows workstations on an air-gapped network by writing an Ansible playbook and PowerShell script, saving roughly 90 hours of manual updates per month.
		\item Drafted a white paper for a Docker infrastructure to securely process files using multiple containers, reducing data transfer costs.
		\item Configured a persistent SMB mount with Kerberos authentication in Red Hat Enterprise Linux.
		\item Gained experience with Agile practices by participating in scrum meetings, sprint planning, and sprint retrospectives.
    \end{rSubsection2}

	\begin{rSubsection2}{National Geospatial-Intelligence Agency}{June 2023 - August 2023}{Software Engineer Intern}{St. Louis, MO}
		\item Cleaned Jira backlog of 2400+ tickets using Python, eliminating 100+ duplicate items and creating visualizations of the data with matplotlib.
		\item Redesigned a Confluence website, creating a more user-friendly design and adding the ability to search and view files in browser.
		\item Automated an accounting procedure using Microsoft Excel, saving about 5 hours of manual work per month.
	\end{rSubsection2}

\end{rSection}

%-----------------------------------------------------------------
%	PROJECTS SECTION
%-----------------------------------------------------------------

\begin{rSection}{Projects}

    % \begin{rProject}{UA Libraries Scholarly API Cookbook}{Python (Matplotlib, NumPy, Pandas, GeoPandas), R}{}
    %     \item Published 20+ tutorials detailing how to access and analyze data from REST APIs for the University of Alabama Libraries.
    %     \item Reviewed tutorials written by other student writers and proactively sought out new APIs to expand the site's coverage.
    % \end{rProject}

	\begin{rProject}{Personal Website}{React, HTML, CSS, Bootstrap}{mtmoen.com}
		\item Designed a website using React, HTML, CSS, and Bootstrap to create a responsive, professional, and mobile-friendly interface.
	\end{rProject}

	\ifthenelse{\boolean{Data}}{
		\begin{rProject}{Air Quality vs. Life Expectancy Analysis}{R, Python (Pandas)}{}
			\item Analyzed U.S. county-level data to evaluate the relationship between air quality indicators and cause-specific mortality rates.
			\item Joined and cleaned datasets from multiple sources using Python, performing exploratory data analysis and model diagnostics in R.
			\item Built multiple linear regression models with variable selection and multicollinearity checks using R to identify key pollutants.
		\end{rProject}
	}{}

	\ifthenelse{\boolean{Backend}}{
		\begin{rProject}{Penny: An AI Chatbot Assistant for Saving Money}{Python (Flask, Plotly)}{}
			\item Created an application using the OpenAI API and Python Flask to advise customers how to reduce spending based on their transactions.
			\item Won 1st place out of ten teams in the Fintech category at the UA Innovate Hackathon, winning the \$1000 grand prize.
		\end{rProject}
	}{}

	\ifthenelse{\boolean{Backend}}{
		\begin{rProject}{CashCourse: A Financial Literacy Education Tool}{Python (FastAPI, Plotly)}{}
			\item Used Python FastAPI endpoints to create Plotly figures, analyze documents, and customize educational materials with the OpenAI API.
		\end{rProject}
	}{}

	\ifthenelse{\boolean{Backend}}{
		\begin{rProject}{Data Structures Library}{C++}{}
			\item Implemented circular dynamic arrays, red-black trees, and Fibonacci heaps in C++ using templates for compatibility with various classes.
		\end{rProject}
	}{}

\end{rSection}

%-----------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%-----------------------------------------------------------------

\begin{rSection}{Skills}

    \renewcommand{\arraystretch}{1.2}
    \begin{tabular}{@{} >{\bfseries}p{2.2cm} p{15.8cm} @{}}
		Languages & Python, C++, R, JavaScript, HTML, CSS, SQL, LaTeX
		% Libraries & NumPy, Pandas, Matplotlib, Flask, Plotly, GeoPandas \\
		\\ Frameworks & FastAPI, scikit-learn, React, Flask, Bootstrap
		\\ Tools & Git, GitHub, Linux, Jira, Confluence, WordPress, Microsoft Office
		% \\ Statistics & Regression, Decision Trees, Neural Networks, Data Visualization, Hypothesis Testing
		% \\ Development & Object-Oriented Programming, Full-Stack Web Development, Software Development, Geographic Information Systems (GIS), Agile Methodologies (Kanban, Scrum)
	\end{tabular}

\end{rSection}

\end{document}
